---
title: "R Notebook"
output: html_notebook
---


```{r}
library(readxl)
pilot_data <- read_excel("191127_PILOT_PTR.xlsx", skip = 9)
library(tidyverse)
```

## Selecting list of targeted chemicals from pilot samples

### Step 1. Obtain average concentration of each chemical during the blank period (aka background concentration) and application period
```{r}
averages <- mutate(pilot_data[1:167],)

# select the subset of rows that correspond to the blank period
# take the column-wise average (average by chemical) (background concentration)
# transpose and add as first column of dataframe to store averages

# select the susbet of rows that correspond to the application period
# take the column-wise average (average by chemical)
# transpose and add as second column of dataframe to store averages

```

### Step 2. Subtract background concentration of each chemical during the blank period from the average during the application period to produce normalized average concentrations for application period
```{r}
#subtract average application from background average for each chemical (vector/array operation) - subtract column 1 from column 2 in the averages df, store result as column 3
```

### Step 4. Sum the normalized average concentration of all chemicals to obtain total normalized average concentration
```{r}

```

### Step 5. Divide the avg normalized concentration for each chemical by the total average normalized concentration to obtain relative abunance of each chemical attributable to the application. This should be a vector (column) of percentages, with length equal to the total number of chemicals, and the values should sum to 100%
```{r}

```

### Sort the list of chemicals by relative abundance, choose the value of N based on a justifiable criterion (input from Randy? Choose the N that accounts for >50%, >90%, etc.)
```{r}

```

```{r}

```

```{r}

```

```{r}

```
